\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Updated eye-tracking apparatus

%On the other hand, educational robots can be of great use in making young school
%kids interested in technological developments~\cite{cooper1999robots,
%wyffels2010building}. It is important to know about the key socio-cognitive
%features of this subset of human-robot interaction because these features let
%the researchers design better interactive scenarios in the future. These
%features include the conceptual mapping of the sensor data visualisation and the
%robot's function and the generalising the concepts to solve a given problem in a
%contextual learning environment.
%
%Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
%attention through the LEDs. We can use this feature to guide the users'
%attention in a way that the effectiveness of the interaction is maximised. In
%the case of interaction with the educational robots the effect of the
%interaction is to make the users understand the technical aspects of the robot
%and to make the users be able to transfer it to different domains.

%Our working hypothesis is that with careful mapping between the LED
%visualisations and the behaviour of the robot we can induce the understanding of
%the functionality of the robot very easily. We propose to use the gaze data to
%verify this hypothesis. With eye-tracking data we can judge whether the mapping
%between the behaviour and visual actuators is useful or not for the participants'
%understanding.  Moreover, we hypothesise that the good performers will be able
%to anticipate the robot's motion. Eye-tracking data can also be useful to verify
%the anticipation hypothesis.
%
%The experiment consists in two phases. The first phase is the observation phase
%during which the participants watch the robot move and detect an obstacle in a
%``playground''. The second phase requires the participants to interact with the
%robot by placing an obstacle in its path to make it detect the obstacle before
%reaching a certain target.  After each phase the participant explain the
%behaviour of the robot. The sensor data was visualised through LEDs with three
%visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
%visualisation. Through this experiment we investigate the following research
%questions:
%
%\begin{enumerate}
%    \item Are there different gaze patterns for different levels of performance
%during the interaction? Moreover, can we see any anticipation patterns
%for the good performers?
%
%    \item How does displaying the sensor information on the robot' body as a
%visual cue affects the gaze and performance of the participants?
%\end{enumerate}
%
%The rest of the paper is organised as follows. The second section gives
%a brief review of the eye-tracking research done to quantify the
%expertise and performance. The third section presents the specificities
%of the study. The fourth section lists the main results. The fifth
%section discusses the results. Finally, the sixth section concludes the
%paper.

@@

\subsection{Eye-tracking}

@@

\fixme{tell about the spatial and temporal resolution of different eye-trackers}

\begin{enumerate}
\item Stationary
\item Mobile 
\item Dual eye-tracking

@@

\item Saccades and transitions
\item Smooth Pursuit
\item Areas of Interest
\item Heat-maps

@@

%We had two measures of performance. First measure was a rating given to
%the responses that participants gave to the question about the
%functionality of the robot. Second measure was the distance from the
%target in the interaction phase.

%We transcribed the responses to perform a rating scheme on the level of
%abstraction and correctness. A low level of abstraction consists in
%describing the functionality of the robot in the terms of the electric
%or programming aspects of the robot, a high level represents describing
%the behaviour. For the levels of correctness, we categorised the
%responses into correct or incorrect response. In TABLE I. we present
%sample responses for the different categories.

%\begin{table}[ht!]
%    \centering
%    \footnotesize
%    \begin{tabular}{ccp{4.5cm}}
%        \toprule
%        Correct. & Abstract. & Sample answer \\
%        \midrule
%        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
%        \midrule
%        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
%        robot turn really early.''\\ 
%        \midrule
%        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
%        the robot sends light. At a certain threshold the robot turns.'' \\ 
%        \midrule
%        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
%        more reflective, and better detectable.''\\ 
%        \bottomrule
%    \end{tabular}
%    \caption{Sample answers for all classes}
%
%    \label{sample_answer}
%\end{table}

@@

%Incorrect answers were further classified into 4 categories; we present
%each category accompanied by a sample response:
%
%\begin{itemize}
%    \item The participant did not respond or offer a possible explanation: ``I
%        really don't know how the robot works''.
%
%    \item The participant identified a wrong cause for the behaviour of the robot:
%        ``The robot notices the tags on the side''.
%
%    \item The participant held the code responsible for the cause of different
%        behaviour: ``The robot turns at a given distance in respect to a color,
%        defined in the program''.
%
%    \item The participant tried to explain by analogies or did not explain the
%        robots behaviour at an understandable level: ``Grey is the most
%        dangerous, so the robot turns really early''.
%
%\end{itemize}

@@

%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
%being better performers than the {\sf TRUE} condition during the interaction phase
%comes from the transparency of the robot's behaviour. The robot's
%behaviour was not at all transparent in the former two conditions. This might
%have caused the participants to put more effort in understanding the behaviour.
%Therefore, they performed better.

>>>>

@@

\subsection{Eye-tracking}
First, we introduce the basic eye-tracking setups, technical steps in mobile eye-tracking and different use cases of mobile eye-tracking.

@@

Most eye trackers work by projecting infrared light on the pupil and measuring the reflection with one or more cameras. . Following are the typical setups for the eye-trackers used in research:

\begin{enumerate}
\item Stationary: The stationary eye-trackers are widely used for the controlled laboratory experiments. These eye-trackers have a separate eye-tracking device (camera, infrared source and microprocessor) and a monitor or a monitor embedded with different parts  of the eye-tracking devices. The data rate is usually higher than the mobile eye-trackers (ranging between 60 Hz to 2000 Hz). The accuracy of current devices is about 0.5 degrees, which correspond to 0.35 mm for a user whose head is placed at 40 cm from the screen.  The setup needs the heads of the participants to be fixed using a opthalmologic head rest for better data quality.

\item Mobile: Mobile eye-trackers are useful to conduct more ecologically valid and naturalistic experiments. These eye-trackers have a scene camera in the front to record the visual field of the participants. Present mobile eye-trackers have a data rate of 30 Hz and a spatial accuracy equal to the stationary eye-trackers.

\item Dual eye-tracking: Dual eye-tracking requires synchronisation of two eye-trackers, so that the researchers can record the gaze data for a pair of collaborators without any lag (as the clocks of two systems can not be perfectly synchronised). \cite{nussli2011dual} explored and compared different ways to synchronise two eye-trackers.

@@

\item Saccades and transitions: Two fixations are connected by a saccade. Saccades are the sudden variations in the eye-movements. While analysing saccades, there are two 
\item Smooth Pursuit
\item Areas of Interest
\item Heat-maps

@@

@@

@@
